Sequential rank agreement methods for comparison of lists

### 2015-07-09 latex/paper.Rnw
started editing the abstract

\title{Sequential rank agreement methods for comparison of ranked
  lists}
\author{Claus Thorn Ekstrøm}
\author{Thomas Alexander Gerds}
\author{Andreas Kryger Jensen}
\author{Kasper Brink-Jensen}
\affil{Biostatistics, University of Copenhagen}

\renewcommand{\topfraction}{.85}
\renewcommand{\bottomfraction}{.7}
\renewcommand{\textfraction}{.15}
\renewcommand{\floatpagefraction}{.66}
\renewcommand{\dbltopfraction}{.66}
\renewcommand{\dblfloatpagefraction}{.66}
\setcounter{topnumber}{9}
\setcounter{bottomnumber}{9}
\setcounter{totalnumber}{20}
\setcounter{dbltopnumber}{9}

@@

\begin{abstract}
  The comparison of ranked lists has been studied for several decades
  but since the advent of large data types it has received increased
  interest. Computer science and genomics are just two areas that need
  to compare ranked lists in order to investigate similarities
  between different analytical methods. Often the aim is to find a
  measure of similarity for two or more ordered lists that comprise
  the first k items from each list. Since ordered lists typically are
  more similar at the top of the list another approach, which is taken
  in this paper is to ask: for how long are the lists highly similar?
  Using terminology from agreement analysis we derive the measure
  depth of agreement using the standard deviation of the ranks, a
  method that both provides an intuitive interpretation and can be
  applied to any number of lists even if these are incomplete. The
  finding are illustrated using simulations and applied to a publicly
  available cancer dataset.
\end{abstract}

@@

<<echo=FALSE>>=
#note: always pass alpha on the 0-255 scale
makeTransparent<-function(someColor, alpha=100)
{
  newColor<-col2rgb(someColor)
  apply(newColor, 2, function(curcoldata){rgb(red=curcoldata[1], green=curcoldata[2],
    blue=curcoldata[3],alpha=alpha, maxColorValue=255)})
}

>>>>

\title{Sequential rank agreement methods for comparison of lists}
\author{Claus Thorn Ekstrøm}
\author{Thomas Alexander Gerds}
\author{Andreas Jensen}
\author{Kasper Brink-Jensen}
\affil{Biostatistics, University of Copenhagen}
\renewcommand{\topfraction}{.85}
\renewcommand{\bottomfraction}{.7}
\renewcommand{\textfraction}{.15}
\renewcommand{\floatpagefraction}{.66}
\renewcommand{\dbltopfraction}{.66}
\renewcommand{\dblfloatpagefraction}{.66}
\setcounter{topnumber}{9}
\setcounter{bottomnumber}{9}
\setcounter{totalnumber}{20}
\setcounter{dbltopnumber}{9}

@@

\begin{abstract}
  The comparison of rankings has received increased interest in the
  last decades. Computer science and genomics are just two areas that
  need to compare ranked lists in order to investigate similarities
  between different analytical methods. Often the aim is to find a
  measure of similarity for two or more ordered lists that comprise
  the first k items from each list. Since ordered lists typically are
  more similar at the top of the list another approach, which is taken
  in this paper is to ask: for how long are the lists highly similar?
  Using terminology from agreement analysis we derive the measure
  depth of agreement using the standard deviation of the ranks, a
  method that both provides an intuitive interpretation and can be
  applied to any number of lists even if these are incomplete. The
  finding are illustrated using simulations and applied to a publicly
  available cancer dataset.
\end{abstract}

@@

<<echo=FALSE>>=
#note: always pass alpha on the 0-255 scale
makeTransparent<-function(someColor, alpha=100)
{
  newColor<-col2rgb(someColor)
  apply(newColor, 2, function(curcoldata){rgb(red=curcoldata[1], green=curcoldata[2],
    blue=curcoldata[3],alpha=alpha, maxColorValue=255)})
}
@ %
